Differences from our PPoPP Conference Paper \cite{KBP16}

### 2018-09-07 latex/toms/experiments.tex
uniform plot was using lowrank details

%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{4.9}
\renewcommand{\ymin}{0}
\renewcommand{\ymax}{.25}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\tikzsetnextfilename{accuracylr81k32}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\tikzsetnextfilename{accuracylr81k64}
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\tikzsetnextfilename{accuracylr81k96}
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Low Rank Tensor of size 129x129x129x129 on 3x3x3x3 Processor Grid.}
\label{fig:convergencelowrank}
\end{figure}

\begin{figure}
%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{9.9}
\renewcommand{\ymin}{.4}
\renewcommand{\ymax}{.52}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\tikzsetnextfilename{accuracylr81k32}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\tikzsetnextfilename{accuracylr81k64}
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\tikzsetnextfilename{accuracylr81k96}
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Uniform Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid.}
\label{fig:convergenceuniform}
\end{figure}

>>>>

%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{4.9}
\renewcommand{\ymin}{0}
\renewcommand{\ymax}{.25}
\subfloat[Low rank $k=32$ \label{fig:accuracylr81k32}]{
\tikzsetnextfilename{accuracylr81k32}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracylr81k64}]{
\tikzsetnextfilename{accuracylr81k64}
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracylr81k96}]{
\tikzsetnextfilename{accuracylr81k96}
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracylr81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Low Rank Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid.}
\label{fig:convergencelowrank}
\end{figure}

\begin{figure}
%set which run to plot
\renewcommand{\run}{32}
\renewcommand{\xmax}{9.9}
\renewcommand{\ymin}{.4}
\renewcommand{\ymax}{.52}
\subfloat[Low rank $k=32$ \label{fig:accuracyuni81k32}]{
\tikzsetnextfilename{accuracyuni81k32}
\ylabeltrue
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{32}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\subfloat[Low rank $k=64$ \label{fig:accuracyuni81k64}]{
\tikzsetnextfilename{accuracyuni81k64}
\widertrue
\legendfalse
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{64}
\relerrplot
\end{tikzpicture}
}
\subfloat[Low rank $k=96$ \label{fig:accuracyuni81k96}]{
\tikzsetnextfilename{accuracyuni81k96}
\ylabeltrue
\widertrue
\legendtrue
\begin{tikzpicture}
\renewcommand{\datafile}{data/accuracyuni81pksweep.csv}
\renewcommand{\run}{96}
\relerrplot
\end{tikzpicture}
\ylabelfalse
}
\caption{Relative error comparison of \MU, \HALS, \BPP\, \ADMM, \Nestrov\ on 4D Synthetic Uniform Tensor of size 162x162x162x162 on 3x3x3x3 Processor Grid.}
\label{fig:convergenceuniform}
\end{figure}
